---
title: "260928_bmk1_ABa-EMS_4-cell"
author: "Sam Zavislan-Pullaro"
date: "2026-09-28"
output: 
  github_document:
    toc: true
    toc_depth: 4
---

## Overview

This analysis compares the log2 fold enrichment of erm-1 at the ABa - EMS membrane during the 4-cell stage of embryonic development in C. elegans. 

Empty vector RNAi control = L4440 

RNAi knockdown condition = bmk-1 

## load libraries

```{r setup, echo = TRUE, warning = FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
library(data.table)
library(rstatix)
library(dplyr)

```


## Import the data that was outputted from the new macro:

Note: 

channel 1 = set-3

channel 2 = erm-1

```{r macroimport, echo = TRUE, warning = FALSE, message = FALSE}

# import the control data
# control data comes from L4440 empty vector RNAi controls 
control_1 <- read.table(file = "../01_input/2026-7-11_1329_datafile_for_231107_LP306_L4440.txt", header = FALSE, sep = "\t")
control_2 <- read.table(file = "../01_input/2026-7-11_1257_datafile_for_230713_L4440_RNAi_rep1.txt", header = FALSE, sep = "\t")
control_3 <- read.table(file = "../01_input/2026-7-11_1311_datafile_for_230828_L4440_RNAi_rep2.txt", header = FALSE, sep = "\t")
control_4 <- read.table(file = "../01_input/2026-7-11_1346_datafile_for_240122_LP306_L4440-rep3.txt", header = FALSE, sep = "\t")


# import RNAi treatment data 
test_1 <- read.table(file = "../01_input/2026-7-14_1233_datafile_for_220719_LP306_bmk-1_RNAi.txt", header = FALSE, sep = "\t")
test_2 <- read.table(file = "../01_input/2026-7-14_1238_datafile_for_230408_LP306_BMK-1_rep1.txt", header = FALSE, sep = "\t")
test_3 <- read.table(file = "../01_input/2026-7-14_1241_datafile_for_231107_LP306_BMK-1_rep2.txt", header = FALSE, sep = "\t")
test_4 <- read.table(file = "../01_input/2026-7-14_1244_datafile_for_231113_LP306_BMK-1_rep3.txt", header = FALSE, sep = "\t")

# test its dimensions
#dim(control_1)
#dim(control_2)
#dim(test_1)
#dim(test_2)
#dim(test_3)
#dim(test_4)

# Rename the column names
col_times <- paste(rep(1:333), sep = "")
colnames(control_1) <- c("file", "channel", col_times)
colnames(control_2) <- c("file", "channel", col_times)
colnames(control_3) <- c("file", "channel", col_times)
colnames(control_4) <- c("file", "channel", col_times)

colnames(test_1) <- c("file", "channel", col_times)
colnames(test_2) <- c("file", "channel", col_times)
colnames(test_3) <- c("file", "channel", col_times)
colnames(test_4) <- c("file", "channel", col_times)

# Check that the dimensions remain unchanged
dim(control_1)
dim(control_2)
dim(control_3)
dim(control_4)

dim(test_1)
dim(test_2)
dim(test_3)
dim(test_4)


# control_1[1:9,1:8]
# control_2[1:9,1:8]
# control_3[1:9,1:8]

# test_1[1:9,1:8]
# test_2[1:9,1:8]
# test_3[1:9,1:8]
# test_4[1:9,1:8]

```


## Create annotation columns

```{r annotationcolumns, echo = TRUE, warning = FALSE, message = FALSE}

# Extract out the salient information from the filename and pivot the data longer - "permed" version
# Had to manually change image names to follow convention/consistency (date_strain_treatment_ID_R3D.dv)

control_1_exp <- control_1[2:dim(control_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_2_exp <- control_2[2:dim(control_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_3_exp <- control_3[2:dim(control_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

control_4_exp <- control_4[2:dim(control_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

 
test_1_exp <- test_1[2:dim(test_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_2_exp <- test_2[2:dim(test_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_3_exp <- test_3[2:dim(test_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_4_exp <- test_4[2:dim(test_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

```

```{r}
# Add in the timepoints

addInTimepoints <- function(tibble) {
  timepoints <- as.vector(unlist(control_1[1,3:335]))
  repnumb = dim(tibble)[1]/333
  tibble::add_column(tibble, timepoints = rep(timepoints,repnumb), .after = "xpoint")
}

control_1_plustime <- addInTimepoints(control_1_exp)
control_2_plustime <- addInTimepoints(control_2_exp)
control_3_plustime <- addInTimepoints(control_3_exp)
control_4_plustime <- addInTimepoints(control_4_exp)

test_1_plustime <- addInTimepoints(test_1_exp)
test_2_plustime <- addInTimepoints(test_2_exp)
test_3_plustime <- addInTimepoints(test_3_exp)
test_4_plustime <- addInTimepoints(test_4_exp)

#check it
control_1_plustime[330:340,]
control_2_plustime[330:340,]
control_3_plustime[330:340,]
control_4_plustime[330:340,]
test_1_plustime[330:340,]
test_2_plustime[330:340,]
test_3_plustime[330:340,]
test_4_plustime[330:340,]
```

```{r}
# Merge the datasets together 
bmk1_RNAi_data_total <- rbind(control_1_plustime, control_2_plustime, control_3_plustime, control_4_plustime, test_1_plustime, test_2_plustime, test_3_plustime, test_4_plustime)

head(bmk1_RNAi_data_total)

# Plot all samples
ggplot(data = bmk1_RNAi_data_total, aes(x = timepoints, y = intensity, group = c(unique_id))) +
  geom_line(aes(colour = unique_id))+
  facet_wrap(~ channel + treatment)+
  guides(color = "none")+
  theme_bw()

```

## Fixed coordinate method

Peak intensity alignment is not used in this analysis. Aligning each embryo to its own
observed channel-2 peak risks manufacturing apparent enrichment at the
alignment point. Instead, every embryo uses the same fixed coordinate system
based on its row position (`xpoint`), re-centered so it spans the same
`-166:166` range. Position 0 is the center of the ROI box from the FIJI macro quantification script. The center of the ROI box was manually aligned to the membrane, using a PH::GFP membrane marker strain to visualize the membrane. 

```{r splitmerge, echo = TRUE, warning = TRUE, message = TRUE}

bmk1_dt <- as.data.table(bmk1_RNAi_data_total)
bmk1_dt$xpoint <- as.integer(bmk1_dt$xpoint)

# Fixed coordinate: recenter xpoint (1:333) to run -166:166, identical for
# every embryo and every channel - no peak-finding, no per-embryo offset.
bmk1_dt[, aligned_row := xpoint - 167]

# Check that everything worked
dim(bmk1_RNAi_data_total)
dim(bmk1_dt)
range(bmk1_dt$aligned_row)

# Rename to match the variable name the rest of the script expects
total_align_long <- bmk1_dt %>%
  select(strain, aligned_row, unique_id, intensity)

```

```{r}
# Data-completeness check: for each position in the fixed coordinate
# (aligned_row, -166:166), count total observations and how many are NA.
# Every embryo covers the full -166:166 range with real values, so
# pct_na should be 0 throughout. Non-zero values would flag missing
# data in the raw macro output.

total_align_long %>%
  group_by(aligned_row) %>%
  summarize(
    n_total = n(),
    n_na = sum(is.na(intensity)),
    pct_na = mean(is.na(intensity)) * 100
  ) %>%
  arrange(aligned_row) %>%
   head()

```
## Generate .csv of max intensities for erm-1 in bmk-1 KD and L4440 control 

End of script: saves and exports to ../03_output directory 

```{r}
max_intensities <- total_align_long %>%
  filter(!grepl("ch1", unique_id)) %>% # filter out rows that contain set-3 in ch1
  group_by(unique_id) %>%
  slice_max(intensity, n = 1, with_ties = FALSE)
```


## re-arrange the dataset and calculate the means 

```{r meanplot, echo = TRUE, warning = FALSE, message = FALSE}
# Normalize the data by dividing by the embryo-specific mean
bmk1_norm_total <- total_align_long %>%
  separate_wider_delim(unique_id, delim = "_", names = c("date", NA, "treatment", "embryoID", "channel")) %>%
  group_by(date, embryoID, channel, treatment) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE))
table(bmk1_norm_total$channel, bmk1_norm_total$treatment)

head(bmk1_norm_total)

```
## Visualize how normalization is affecting y-axis

```{r}
normalized_linescan <- ggplot(data = bmk1_norm_total, aes(x = aligned_row, y = normalized_intensity, 
                                     group = interaction(date, embryoID, channel))) +
  geom_line(aes(color = interaction(date, embryoID, channel)), alpha = 0.5) +
  facet_wrap(~ channel + treatment) +
  guides(color = "none") +
  theme_bw()

normalized_linescan
```

```{r}
# Separate out the unique identifier info, then pivot sider
bmk1_wide_by_sample <- bmk1_norm_total %>%
  pivot_wider(names_from = c(date, embryoID, channel, treatment), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row))


# Second Try - Separate out the unique identifier info, then pivot sider
bmk1_wide_by_sample <- bmk1_norm_total %>%
  pivot_wider(names_from = c(date, embryoID), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row, treatment, channel))

colnames(bmk1_wide_by_sample)

# Play around with mean, medium, and sum:
bmk1_wide_with_stats <- bmk1_wide_by_sample %>%
  rowwise() %>%
  mutate(
    sum_signal    = sum(c_across(`231107_02`:`231113_02`), na.rm = TRUE),
    mean_signal   = mean(c_across(`231107_02`:`231113_02`), na.rm = TRUE),
    median_signal = median(c_across(`231107_02`:`231113_02`), na.rm = TRUE),
    sd_signal     = sd(c_across(`231107_02`:`231113_02`), na.rm = TRUE)
  ) %>%
  ungroup()

# colnames(bmk1_wide_with_stats)

bmk1_wide_with_range <- bmk1_wide_with_stats %>%
  rowwise() %>%
  mutate(ymeanmax = sum(mean_signal, sd_signal) ) %>%
  mutate(ymeanmin = sum(mean_signal, -sd_signal)) %>%
  ungroup() %>%
  mutate(treatment = factor(treatment, levels = c("L4440", "bmk-1")))

colorselection = c("#000000", "#2189ce")

# Plot split by RNAi treatment and L4440 empty vector control 
a <- ggplot(data = bmk1_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=channel))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("set-1 mRNA", "erm-1 mRNA"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=channel), alpha = 0.2, ) +
  facet_wrap(~ treatment)+
  theme_bw()

a


# Plot in a different way - set-3 and erm-1 mRNA split into facets
colorselection = c("#2189ce", "#000000")
channel.labs <- c("set-3 mRNA", "erm-1 mRNA")
names(channel.labs) <- c("ch1", "ch2")

# Plot split by transcript
b <- ggplot(data = bmk1_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=treatment))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("control", "bmk-1 RNAi"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=treatment), alpha = 0.2, ) +
  facet_wrap(~ channel, labeller = labeller(channel = channel.labs))+
  theme_bw()

```

## Create a metric of "membrane-y-ness" for each condition

We are comparing the log2 fold change intensity at the membrane to the flanking regions along the anterior to posterior axis

For 2-cell stage, we used the range: -100,0,100

For 4-cell stage, use -50,0,50 range because the cells are smaller, and the orientation of the membrane can push the ROI quantification box outside of the embryo. 

```{r membraneyness, echo = TRUE, warning = FALSE, message = FALSE, fig.width = 6, fig.height = 6}

# # extract the peak intensity versus the -50 and +50 values
# peaks_and_valleys <- bmk1_norm_total %>%
#   filter(aligned_row %in% c(-50,0,50))
# 
# # Nest the -50, 1, and +50 values
# nest_pandv <- peaks_and_valleys %>%
#   group_by(date, treatment, embryoID, channel) %>%
#   nest()
# 
# # A function to calculate the ratio of the value at 1 compared to the mean of positions, -50 and +50
# my_calc2 <- function(df) {
#   df$normalized_intensity[2] / mean(c(df$normalized_intensity[1], df$normalized_intensity[3]))
# }
# 
# # Calculate the ratio for each datapoint
# foldChange_calc <- nest_pandv %>%
#   mutate(fc_enrich = map_dbl(data, my_calc2))
# 
# # Change some columns to factors
# foldChange_calc$treatment <- factor(foldChange_calc$treatment, levels = c("L4440", "bmk-1")) 
# foldChange_calc$channel <- as.factor(foldChange_calc$channel)
# 
# 
# # plot the data:
# d <- ggplot(data = foldChange_calc, aes(x = as.factor(channel), y = log(fc_enrich, base = 2), fill = treatment))+
#   geom_boxplot(outlier.shape = NA)+
#   geom_jitter(position=position_jitterdodge())+
#   scale_y_continuous(limits = c(-0.5, 1.0)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   scale_fill_manual(values = c("L4440" = "darkgray", "bmk-1" = "lightblue"),
#                    labels = c("L4440" = "L4440 control", "bmk-1" = "bmk-1 RNAi"))+labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -50 and 50)", x = "mRNA") +
#   scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
#   theme_classic(base_size = 12)
# 
# d
# 
# e <- ggplot(data = foldChange_calc, aes(x = as.factor(treatment), y = log(fc_enrich, base = 2), fill = channel))+
#   geom_boxplot(outlier.shape = NA)+
#   geom_jitter(position=position_jitterdodge())+
#   scale_y_continuous(limits = c(-0.5, 1.0)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -50 and 50)", x = "mRNA") +
#   theme_classic(base_size = 12)
# 
# #e

```
## Get summary stats for log2 fold change enrichment at membrane vs flanking regions 

```{r}

# foldChange_calc %>%
#   group_by(treatment, channel) %>%
#   summarise(
#     min_log2fc    = min(log(fc_enrich, base = 2), na.rm = TRUE),
#     median_log2fc = median(log(fc_enrich, base = 2), na.rm = TRUE),
#     mean_log2fc   = mean(log(fc_enrich, base = 2), na.rm = TRUE),
#     max_log2fc    = max(log(fc_enrich, base = 2), na.rm = TRUE)
#   )

```

## Calculate the statistics

```{r}
# # Check normality 
# 
# foldChange_calc %>%
#   group_by(treatment, channel) %>%
#   shapiro_test(fc_enrich)
# 
# # QQ plots to visualize normality
# ggplot(foldChange_calc, aes(sample = fc_enrich)) +
#   stat_qq() +
#   stat_qq_line() +
#   facet_wrap(~ treatment + channel) +
#   theme_bw()
```
```{r}
# # Homogeneity of variance across treatment groups, within each channel
# 
# foldChange_calc %>%
#   group_by(channel) %>%
#   levene_test(fc_enrich ~ treatment)
```


```{r wilcox, echo = TRUE, warning = FALSE, message = FALSE}

# foldChange_calc
# 
# stats_wilcox <- foldChange_calc %>%
#   group_by(channel) %>%
#   wilcox_test(fc_enrich ~ treatment) %>%
#   adjust_pvalue(method = "BH") %>%
#   add_significance()
# 
# stats_wilcox

```
```{r}
### Passes normality and equal variance tests 
### Standard t test with var.equal = TRUE is appropriate 

# stats_ttest <- foldChange_calc %>%
#   group_by(channel) %>%
#   t_test(fc_enrich ~ treatment, var.equal = TRUE) %>%
#   group_by(channel) %>%
#   adjust_pvalue(method = "BH") %>%
#   add_significance()
# stats_ttest

```

---

## Window-based "membrane-y-ness" (alternative to single-point fc_enrich)

The metric above (`fc_enrich`) reads a single row for the peak (`aligned_row == 0`)
and single rows for the flanks (`-50`, `50`), so it's sensitive to noise at exactly
those three coordinates. This section averages over a small window around each of
those points instead, which should be less sensitive to single-pixel noise while
staying directly comparable to `fc_enrich` above.

### Calculate the window-based ratio

```{r window_membraneyness, echo = TRUE, warning = FALSE, message = FALSE}

window_half_width <- 5  # rows to either side of each point

peak_flank_windows <- bmk1_norm_total %>%
  mutate(region = case_when(
    aligned_row >= -window_half_width & aligned_row <= window_half_width ~ "peak",
    aligned_row >= -50 - window_half_width & aligned_row <= -50 + window_half_width ~ "flank_left",
    aligned_row >=  50 - window_half_width & aligned_row <=  50 + window_half_width ~ "flank_right",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(region))

fc_window <- peak_flank_windows %>%
  group_by(date, treatment, embryoID, channel, region) %>%
  summarise(mean_intensity = mean(normalized_intensity, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = region, values_from = mean_intensity) %>%
  mutate(flank = (flank_left + flank_right) / 2,   # average the two flank means, not pooled rows
         fc_enrich_window = peak / flank,
         log2_fc_window = log2(fc_enrich_window))

# Same factor setup as the point-based version
fc_window$treatment <- factor(fc_window$treatment, levels = c("L4440", "bmk-1"))
fc_window$channel   <- as.factor(fc_window$channel)

fc_window

```

### Plot the window-based enrichment

```{r window_plot, echo = TRUE, warning = FALSE, message = FALSE, fig.width = 6, fig.height = 6}

d_window <- ggplot(data = fc_window, aes(x = as.factor(channel), y = log2_fc_window, fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 1.0)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("L4440" = "darkgray", "bmk-1" = "lightblue"),
                   labels = c("L4440" = "L4440 control", "bmk-1" = "bmk-1 RNAi"))+
  labs(y = "log2 FoldChange Enrichment of mRNA \n(window-averaged mRNA intensity at 0 / window-averaged mRNA intensity at -50 and 50)", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 12)

d_window

```

### Summary stats

```{r window_summary, echo = TRUE, warning = FALSE, message = FALSE}

window_summary_stats <- fc_window %>%
  group_by(treatment, channel) %>%
  summarise(
    min_log2fc    = min(log2_fc_window, na.rm = TRUE),
    median_log2fc = median(log2_fc_window, na.rm = TRUE),
    mean_log2fc   = mean(log2_fc_window, na.rm = TRUE),
    max_log2fc    = max(log2_fc_window, na.rm = TRUE)
  )

window_summary_stats

```

### Check assumptions

```{r window_assumptions, echo = TRUE, warning = FALSE, message = FALSE}

# Normality
fc_window %>%
  group_by(treatment, channel) %>%
  shapiro_test(fc_enrich_window)

ggplot(fc_window, aes(sample = fc_enrich_window)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ treatment + channel) +
  theme_bw()

# Homogeneity of variance
fc_window %>%
  group_by(channel) %>%
  levene_test(fc_enrich_window ~ treatment)

```

### Statistics

```{r window_stats, echo = TRUE, warning = FALSE, message = FALSE}

# 1) Wilcoxon test

stats_wilcox_window <- fc_window %>%
  group_by(channel) %>%
  wilcox_test(fc_enrich_window ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox_window

# 2) Welch t test with var.equal = TRUE 

stats_ttest_window <- fc_window %>%
  group_by(channel) %>%
  t_test(fc_enrich_window ~ treatment, var.equal = TRUE) %>%
  group_by(channel) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_ttest_window

```

---

## Export plots and stats

```{r export_outputs}

today      <- format(Sys.Date(), "%y%m%d")
output_dir <- "../03_output"
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

ggsave(file.path(output_dir, paste0(today, "_boxplot_window.svg")), plot = d_window,
       width = 6, height = 6)
ggsave(file.path(output_dir, paste0(today, "_linescan_individual.svg")), plot = normalized_linescan,
       width = 6, height = 6)
ggsave(file.path(output_dir, paste0(today, "_mean_signal_linscan.svg")), plot = a,
       width = 6, height = 6)

write_csv(window_summary_stats, file.path(output_dir, paste0(today, "_window_summary_stats.csv")))
write_csv(stats_wilcox_window, file.path(output_dir, paste0(today, "_wilcoxon_stats_window.csv")))
write_csv(stats_ttest_window, file.path(output_dir, paste0(today, "_ttest_stats_window.csv")))

cat("Exported to:", normalizePath(output_dir), "\n")


```

## Session info

```{r sessionInfo, echo = TRUE, warning = FALSE, message = FALSE}

sessionInfo()

```