---
title: "4-cell erm-1 bmk-1 KD analysis"
author: "Sam Zavislan-Pullaro, Erin Osborne Nishimura"
date: "2026-08-26"
output: 
  github_document:
    toc: true
    toc_depth: 4
---

## Overview

This analysis compares the log2 fold enrichment of erm-1 at the ABa - ABp membrane and ABa - EMS membrane during the 4-cell stage of embryonic development in C. elegans. 

Empty vector RNAi control = L4440 

RNAi knockdown condition = bmk-1 

## Load libraries

```{r setup, echo = TRUE, warning = FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
library(data.table)
library(rstatix)
library(dplyr)

```


## Import the data

Note: 

channel 1 = set-3

channel 2 = erm-1

```{r macroimport, echo = TRUE, warning = FALSE, message = FALSE}

# import the control data
# control data comes from L4440 empty vector RNAi controls 

# ABa - ABp 
control_1 <- read.table(file = "../01_input/2026-7-11_1324_datafile_for_231107_LP306_L4440.txt", header = FALSE, sep = "\t")
control_2 <- read.table(file = "../01_input/2026-7-11_1252_datafile_for_230713_L4440_RNAi_rep1.txt", header = FALSE, sep = "\t")
control_3 <- read.table(file = "../01_input/2026-7-11_133_datafile_for_230828_L4440_RNAi_rep2.txt", header = FALSE, sep = "\t")
control_4 <- read.table(file = "../01_input/2026-7-11_1337_datafile_for_240122_LP306_L4440-rep3.txt", header = FALSE, sep = "\t")


# import RNAi treatment data 
test_1 <- read.table(file = "../01_input/2026-7-14_126_datafile_for_220719_LP306_bmk-1_RNAi.txt", header = FALSE, sep = "\t")
test_2 <- read.table(file = "../01_input/2026-7-14_1216_datafile_for_230408_LP306_BMK-1_rep1.txt", header = FALSE, sep = "\t")
test_3 <- read.table(file = "../01_input/2026-7-14_1222_datafile_for_231107_LP306_BMK-1_rep2.txt", header = FALSE, sep = "\t")
test_4 <- read.table(file = "../01_input/2026-7-14_1225_datafile_for_231113_LP306_BMK-1_rep3.txt", header = FALSE, sep = "\t")

# ABa - EMS
control_5 <- read.table(file = "../01_input/2026-7-11_1329_datafile_for_231107_LP306_L4440.txt", header = FALSE, sep = "\t")
control_6 <- read.table(file = "../01_input/2026-7-11_1257_datafile_for_230713_L4440_RNAi_rep1.txt", header = FALSE, sep = "\t")
control_7 <- read.table(file = "../01_input/2026-7-11_1311_datafile_for_230828_L4440_RNAi_rep2.txt", header = FALSE, sep = "\t")
control_8 <- read.table(file = "../01_input/2026-7-11_1346_datafile_for_240122_LP306_L4440-rep3.txt", header = FALSE, sep = "\t")


# import RNAi treatment data 
test_5 <- read.table(file = "../01_input/2026-7-14_1233_datafile_for_220719_LP306_bmk-1_RNAi.txt", header = FALSE, sep = "\t")
test_6 <- read.table(file = "../01_input/2026-7-14_1238_datafile_for_230408_LP306_BMK-1_rep1.txt", header = FALSE, sep = "\t")
test_7 <- read.table(file = "../01_input/2026-7-14_1241_datafile_for_231107_LP306_BMK-1_rep2.txt", header = FALSE, sep = "\t")
test_8 <- read.table(file = "../01_input/2026-7-14_1244_datafile_for_231113_LP306_BMK-1_rep3.txt", header = FALSE, sep = "\t")

# Rename the column names
col_times <- paste(rep(1:333), sep = "")

# ABa - ABp
colnames(control_1) <- c("file", "channel", col_times)
colnames(control_2) <- c("file", "channel", col_times)
colnames(control_3) <- c("file", "channel", col_times)
colnames(control_4) <- c("file", "channel", col_times)

colnames(test_1) <- c("file", "channel", col_times)
colnames(test_2) <- c("file", "channel", col_times)
colnames(test_3) <- c("file", "channel", col_times)
colnames(test_4) <- c("file", "channel", col_times)

# ABa - EMS
colnames(control_5) <- c("file", "channel", col_times)
colnames(control_6) <- c("file", "channel", col_times)
colnames(control_7) <- c("file", "channel", col_times)
colnames(control_8) <- c("file", "channel", col_times)

colnames(test_5) <- c("file", "channel", col_times)
colnames(test_6) <- c("file", "channel", col_times)
colnames(test_7) <- c("file", "channel", col_times)
colnames(test_8) <- c("file", "channel", col_times)

# Check that the dimensions remain unchanged
dim(control_1)
dim(control_2)
dim(control_3)
dim(control_4)

dim(test_1)
dim(test_2)
dim(test_3)
dim(test_4)

dim(control_5)
dim(control_6)
dim(control_7)
dim(control_8)

dim(test_5)
dim(test_6)
dim(test_7)
dim(test_8)


# control_1[1:9,1:8]
# control_2[1:9,1:8]
# control_3[1:9,1:8]

# test_1[1:9,1:8]
# test_2[1:9,1:8]
# test_3[1:9,1:8]
# test_4[1:9,1:8]

```


## Create annotation columns

```{r annotationcolumns, echo = TRUE, warning = FALSE, message = FALSE}

# Extract out the salient information from the filename and pivot the data longer
# Had to manually change image names to follow convention/consistency
# Imaging date in the first field and embryo ID # remained unchanged

# ABa - ABp
control_1_exp <- control_1[2:dim(control_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_2_exp <- control_2[2:dim(control_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_3_exp <- control_3[2:dim(control_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

control_4_exp <- control_4[2:dim(control_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

 
test_1_exp <- test_1[2:dim(test_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_2_exp <- test_2[2:dim(test_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_3_exp <- test_3[2:dim(test_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_4_exp <- test_4[2:dim(test_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

# ABa - EMS
control_5_exp <- control_5[2:dim(control_5)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_6_exp <- control_6[2:dim(control_6)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_7_exp <- control_7[2:dim(control_7)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

control_8_exp <- control_8[2:dim(control_8)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

 
test_5_exp <- test_5[2:dim(test_5)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_6_exp <- test_6[2:dim(test_6)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_7_exp <- test_7[2:dim(test_7)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_8_exp <- test_8[2:dim(test_8)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

```

## Add timepoints as proxy for position along anterior to posterior axis 

```{r}
# Add in the timepoints

addInTimepoints <- function(tibble) {
  timepoints <- as.vector(unlist(control_1[1,3:335]))
  repnumb = dim(tibble)[1]/333
  tibble::add_column(tibble, timepoints = rep(timepoints,repnumb), .after = "xpoint")
}

# ABa - ABp
control_1_plustime <- addInTimepoints(control_1_exp)
control_2_plustime <- addInTimepoints(control_2_exp)
control_3_plustime <- addInTimepoints(control_3_exp)
control_4_plustime <- addInTimepoints(control_4_exp)

test_1_plustime <- addInTimepoints(test_1_exp)
test_2_plustime <- addInTimepoints(test_2_exp)
test_3_plustime <- addInTimepoints(test_3_exp)
test_4_plustime <- addInTimepoints(test_4_exp)

# ABa - EMS
control_5_plustime <- addInTimepoints(control_5_exp)
control_6_plustime <- addInTimepoints(control_6_exp)
control_7_plustime <- addInTimepoints(control_7_exp)
control_8_plustime <- addInTimepoints(control_8_exp)

test_5_plustime <- addInTimepoints(test_5_exp)
test_6_plustime <- addInTimepoints(test_6_exp)
test_7_plustime <- addInTimepoints(test_7_exp)
test_8_plustime <- addInTimepoints(test_8_exp)

#check it

# ABa - ABp 
control_1_plustime[330:340,]
control_2_plustime[330:340,]
control_3_plustime[330:340,]
control_4_plustime[330:340,]
test_1_plustime[330:340,]
test_2_plustime[330:340,]
test_3_plustime[330:340,]
test_4_plustime[330:340,]

# ABa - EMS
control_5_plustime[330:340,]
control_6_plustime[330:340,]
control_7_plustime[330:340,]
control_8_plustime[330:340,]
test_5_plustime[330:340,]
test_6_plustime[330:340,]
test_7_plustime[330:340,]
test_8_plustime[330:340,]
```

```{r}
# Merge the datasets together 
bmk1_RNAi_data_total <- rbind(control_1_plustime, control_2_plustime, control_3_plustime, control_4_plustime, test_1_plustime, test_2_plustime, test_3_plustime, test_4_plustime, control_5_plustime, control_6_plustime, control_7_plustime, control_8_plustime, test_5_plustime, test_6_plustime, test_7_plustime, test_8_plustime)

head(bmk1_RNAi_data_total)

# Plot all samples
ggplot(data = bmk1_RNAi_data_total, aes(x = timepoints, y = intensity, group = c(unique_id))) +
  geom_line(aes(colour = unique_id))+
  facet_wrap(~ channel + treatment)+
  guides(color = "none")+
  theme_bw()

```


## Use fixed coordinate system 

Peak alignment not used in this analysis because. Aligning each embryo to its own
observed channel-2 peak risks manufacturing apparent enrichment at the
alignment point, since by construction that point is the brightest value in
every embryo. Instead, every embryo uses the same fixed coordinate system
based on its row position (`xpoint`), recentered so it spans the same
`-166:166` range.

```{r splitmerge, echo = TRUE, warning = TRUE, message = TRUE}

bmk1_dt <- as.data.table(bmk1_RNAi_data_total)
bmk1_dt$xpoint <- as.integer(bmk1_dt$xpoint)

# Fixed coordinate: recenter xpoint (1:333) to run -166:166, identical for
# every embryo and every channel - no peak-finding, no per-embryo offset.
bmk1_dt[, aligned_row := xpoint - 167]

# Check that everything worked
dim(bmk1_RNAi_data_total)
dim(bmk1_dt)
range(bmk1_dt$aligned_row)

# Rename to match the variable name the rest of the script expects
total_align_long <- bmk1_dt %>%
  select(strain, aligned_row, unique_id, intensity)

```

```{r}
# Data-completeness check: for each position in the fixed coordinate
# (aligned_row, -166:166), count total observations and how many are NA.
# Every embryo covers the full -166:166 range with real values, so
# pct_na should be 0 throughout. Non-zero values would flag missing
# data in the raw macro output.

total_align_long %>%
  group_by(aligned_row) %>%
  summarize(
    n_total = n(),
    n_na = sum(is.na(intensity)),
    pct_na = mean(is.na(intensity)) * 100
  ) %>%
  arrange(aligned_row) %>%
  print(n = Inf)

```

## re-arrange the dataset and calculate the means 

```{r meanplot, echo = TRUE, warning = FALSE, message = FALSE}
# Normalize the data by dividing by the embryo-specific mean
bmk1_norm_total <- total_align_long %>%
  separate_wider_delim(unique_id, delim = "_", names = c("date", NA, "treatment", "embryoID", "channel")) %>%
  group_by(date, embryoID, channel, treatment) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE))
table(bmk1_norm_total$channel, bmk1_norm_total$treatment)

head(bmk1_norm_total)

```

```{r}
# Exclude 220719_12 (ch2) for now - identified as having an atypical
# secondary shoulder before the main peak (color-matched from the
# line-scan plot). Pending review of the raw image; remove this filter
# once resolved, or add more rows to excluded_embryos to drop others.

excluded_embryos <- tibble::tribble(
  ~date,    ~embryoID, ~channel,
  "231107", "13",      "ch2"
)

bmk1_norm_total <- bmk1_norm_total %>%
  anti_join(excluded_embryos, by = c("date", "embryoID", "channel"))

# Confirm removal - counts should drop by one embryo in ch2/bmk-1
table(bmk1_norm_total$channel, bmk1_norm_total$treatment)
```

## Visualize normalized linescans

```{r}
normalized_linescan <- ggplot(data = bmk1_norm_total, aes(x = aligned_row, y = normalized_intensity, 
                                     group = interaction(date, embryoID, channel))) +
  geom_line(aes(color = treatment), alpha = 0.5) +
  scale_color_manual(values = c("#2189ce", "#000000")) +
  facet_wrap(~ channel + treatment) +
  guides(color = "none") +
  theme_bw()
normalized_linescan
```

```{r kinesins_mean_overlaid, fig.height = 3, fig.width = 7}

# treatment_colors <- c(
#   "L4440"   = "darkgray",
#   "bmk-1"   = "lightblue"
# )
# 
# mean_signal <- bmk1_norm_total %>%
#   group_by(aligned_row, treatment, channel) %>%
#   summarize(
#     mean_signal = mean(normalized_intensity, na.rm = TRUE),
#     sd_signal   = sd(normalized_intensity,   na.rm = TRUE),
#     .groups     = "drop"
#   ) %>%
#   mutate(
#     ymeanmax = mean_signal + sd_signal,
#     ymeanmin = mean_signal - sd_signal
#   )
# 
# kinesin_treatments <- c("L4440", "bmk-1")
# 
# channel_labels <- c("ch1" = "set-3 mRNA", "ch2" = "erm-1 mRNA")
# 
# mean_signal_kinesins <- mean_signal %>%
#   filter(treatment %in% kinesin_treatments)
# 
# ggplot(mean_signal_kinesins,
#        aes(x = aligned_row, y = mean_signal,
#            color = treatment, fill = treatment,
#            group = treatment)) +
#   geom_line(linewidth = 0.8) +
#   scale_color_manual(values = treatment_colors) +
#   scale_fill_manual(values  = treatment_colors) +
#   facet_wrap(~ channel, labeller = labeller(channel = channel_labels)) +
#   labs(
#     title  = "Mean normalized 4 -cell line scans - L4440 vs bmk-1 KD",
#     x      = "Position",
#     y      = "Mean normalized intensity",
#     color  = "Treatment",
#     fill   = "Treatment"
#   ) +
#   theme_bw(base_size = 12) +
#   theme(strip.text = element_text(face = "bold"),
#         legend.position = "right")

```

```{r, fig.width=8, fig.height=3}
# Separate out the unique identifier info, then pivot sider
bmk1_wide_by_sample <- bmk1_norm_total %>%
  pivot_wider(names_from = c(date, embryoID, channel, treatment), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row))


# Second Try - Separate out the unique identifier info, then pivot sider
bmk1_wide_by_sample <- bmk1_norm_total %>%
  pivot_wider(names_from = c(date, embryoID), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row, treatment, channel))

colnames(bmk1_wide_by_sample)

# Play around with mean, medium, and sum:
bmk1_wide_with_stats <- bmk1_wide_by_sample %>%
  rowwise() %>%
  mutate(
    sum_signal    = sum(c_across(`231107a_02`:`231113_02`), na.rm = TRUE),
    mean_signal   = mean(c_across(`231107a_02`:`231113_02`), na.rm = TRUE),
    median_signal = median(c_across(`231107a_02`:`231113_02`), na.rm = TRUE),
    sd_signal     = sd(c_across(`231107a_02`:`231113_02`), na.rm = TRUE)
  ) %>%
  ungroup()

# colnames(bmk1_wide_with_stats)

bmk1_wide_with_range <- bmk1_wide_with_stats %>%
  rowwise() %>%
  mutate(ymeanmax = sum(mean_signal, sd_signal) ) %>%
  mutate(ymeanmin = sum(mean_signal, -sd_signal)) %>%
  ungroup() %>%
  mutate(treatment = factor(treatment, levels = c("L4440", "bmk-1")))

colorselection = c("#000000", "#2189ce")

# Plot split by RNAi treatment and L4440 empty vector control 
a <- ggplot(data = bmk1_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment))) +
  geom_line(aes(color = channel)) +
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("set-1 mRNA", "erm-1 mRNA")) +
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill = channel), alpha = 0.2) +
  facet_wrap(~ treatment) +
  scale_y_continuous(breaks = seq(0, 3, by = 0.5)) +
  theme_bw()
a

# Plot in a different way - set-3 and erm-1 mRNA split into facets
colorselection = c("#000000", "#2189ce")
channel.labs <- c("set-3 mRNA", "erm-1 mRNA")
names(channel.labs) <- c("ch1", "ch2")

# Plot split by transcript
b <- ggplot(data = bmk1_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=treatment))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("control", "bmk-1 RNAi"))+
  facet_wrap(~ channel, labeller = labeller(channel = channel.labs))+
  theme_bw()

b

```

## Create a metric of "membrane-y-ness" for each condition

We are comparing the log2 fold change intensity at the membrane to the flanking regions along the anterior to posterior axis

For 2-cell stage, we used the range: -100,0,100

For 4-cell stage, use -50,0,50 range because the cells are smaller, and the orientation of the membrane can push the ROI quantification box outside of the embryo. 

```{r membraneyness, echo = TRUE, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 6}

# extract the peak intensity versus the -50 and +50 values
# peaks_and_valleys <- bmk1_norm_total %>%
#   filter(aligned_row %in% c(-50,0,50))
# 
# # Nest the -50, 1, and +50 values
# nest_pandv <- peaks_and_valleys %>%
#   group_by(date, treatment, embryoID, channel) %>%
#   nest()
# 
# # A function to calculate the ratio of the value at 1 compared to the mean of positions, -50 and +50
# my_calc2 <- function(df) {
#   df$normalized_intensity[2] / mean(c(df$normalized_intensity[1], df$normalized_intensity[3]))
# }
# 
# # Calculate the ratio for each datapoint
# foldChange_calc <- nest_pandv %>%
#   mutate(fc_enrich = map_dbl(data, my_calc2))
# 
# # Change some columns to factors
# foldChange_calc$treatment <- factor(foldChange_calc$treatment, levels = c("L4440", "bmk-1")) 
# foldChange_calc$channel <- as.factor(foldChange_calc$channel)


# plot the data:
# d <- ggplot(data = foldChange_calc, aes(x = as.factor(channel), y = log(fc_enrich, base = 2), fill = treatment))+
#   geom_boxplot(outlier.shape = NA)+
#   geom_jitter(position=position_jitterdodge())+
#   scale_y_continuous(limits = c(-0.5, 1.0)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   scale_fill_manual(values = c("L4440" = "darkgray", "bmk-1" = "lightblue"),
#                    labels = c("L4440" = "L4440 control", "bmk-1" = "bmk-1 RNAi"))+labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -50 and 50)", x = "mRNA") +
#   scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
#   theme_classic(base_size = 12)
# 
# d
# 
# e <- ggplot(data = foldChange_calc, aes(x = as.factor(treatment), y = log(fc_enrich, base = 2), fill = channel))+
#   geom_boxplot(outlier.shape = NA)+
#   geom_jitter(position=position_jitterdodge())+
#   scale_y_continuous(limits = c(-0.5, 1.0)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -50 and 50)", x = "mRNA") +
#   theme_classic(base_size = 12)
# 
# #e


```
## Get summary stats for log2 fold change enrichment at membrane vs flanking regions 

```{r}

# foldChange_calc %>%
#   group_by(treatment, channel) %>%
#   summarise(
#     min_log2fc    = min(log(fc_enrich, base = 2), na.rm = TRUE),
#     median_log2fc = median(log(fc_enrich, base = 2), na.rm = TRUE),
#     mean_log2fc   = mean(log(fc_enrich, base = 2), na.rm = TRUE),
#     max_log2fc    = max(log(fc_enrich, base = 2), na.rm = TRUE)
#   )

```

## Calculate the statistics

```{r}
# # Check normality 
# 
# foldChange_calc %>%
#   group_by(treatment, channel) %>%
#   shapiro_test(fc_enrich)
# 
# # QQ plots to visualize normality
# ggplot(foldChange_calc, aes(sample = fc_enrich)) +
#   stat_qq() +
#   stat_qq_line() +
#   facet_wrap(~ treatment + channel) +
#   theme_bw()
# # Homogeneity of variance across treatment groups, within each channel
# 
# foldChange_calc %>%
#   group_by(channel) %>%
#   levene_test(fc_enrich ~ treatment)
```


```{r wilcox, echo = TRUE, warning = FALSE, message = FALSE}

# foldChange_calc
# 
# stats_wilcox <- foldChange_calc %>%
#   group_by(channel) %>%
#   wilcox_test(fc_enrich ~ treatment) %>%
#   adjust_pvalue(method = "BH") %>%
#   add_significance()
# 
# stats_wilcox


```
```{r}
### Passes normality and equal variance tests 
### Standard t test with var.equal = TRUE is appropriate 

# stats_ttest <- foldChange_calc %>%
#   group_by(channel) %>%
#   t_test(fc_enrich ~ treatment, var.equal = TRUE) %>%
#   group_by(channel) %>%
#   adjust_pvalue(method = "BH") %>%
#   add_significance()
# stats_ttest

```

---

## Window-based "membrane-y-ness" (alternative to single-point fc_enrich)

The metric above (`fc_enrich`) reads a single row for the peak (`aligned_row == 0`)
and single rows for the flanks (`-50`, `50`), so it's sensitive to noise at exactly
those three coordinates. This section averages over a small window around each of
those points instead, which should be less sensitive to single-pixel noise while
staying directly comparable to `fc_enrich` above.

### Calculate the window-based ratio

```{r window_membraneyness, echo = TRUE, warning = FALSE, message = FALSE}

window_half_width <- 5  # rows to either side of each point

peak_flank_windows <- bmk1_norm_total %>%
  mutate(region = case_when(
    aligned_row >= -window_half_width & aligned_row <= window_half_width ~ "peak",
    aligned_row >= -50 - window_half_width & aligned_row <= -50 + window_half_width ~ "flank_left",
    aligned_row >=  50 - window_half_width & aligned_row <=  50 + window_half_width ~ "flank_right",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(region))

fc_window <- peak_flank_windows %>%
  group_by(date, treatment, embryoID, channel, region) %>%
  summarise(mean_intensity = mean(normalized_intensity, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = region, values_from = mean_intensity) %>%
  mutate(flank = (flank_left + flank_right) / 2,   # average the two flank means, not pooled rows
         fc_enrich_window = peak / flank,
         log2_fc_window = log2(fc_enrich_window))

# Same factor setup as the point-based version
fc_window$treatment <- factor(fc_window$treatment, levels = c("L4440", "bmk-1"))
fc_window$channel   <- as.factor(fc_window$channel)

fc_window

```

### Plot the window-based enrichment

```{r window_plot, echo = TRUE, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 6}

d_window <- ggplot(data = fc_window, aes(x = as.factor(channel), y = log2_fc_window, fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 1.0)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("L4440" = "darkgray", "bmk-1" = "lightblue"),
                   labels = c("L4440" = "L4440 control", "bmk-1" = "bmk-1 RNAi"))+
  labs(y = "log2 FoldChange Enrichment of mRNA \n(window-averaged mRNA intensity at 0 / window-averaged mRNA intensity at -50 and 50)", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 12)

d_window

```

### Summary stats

```{r window_summary, echo = TRUE, warning = FALSE, message = FALSE}

fc_window %>%
  group_by(treatment, channel) %>%
  summarise(
    min_log2fc    = min(log2_fc_window, na.rm = TRUE),
    median_log2fc = median(log2_fc_window, na.rm = TRUE),
    mean_log2fc   = mean(log2_fc_window, na.rm = TRUE),
    max_log2fc    = max(log2_fc_window, na.rm = TRUE)
  )

```

### Check assumptions

```{r window_assumptions, echo = TRUE, warning = FALSE, message = FALSE}

# Normality
fc_window %>%
  group_by(treatment, channel) %>%
  shapiro_test(fc_enrich_window)

ggplot(fc_window, aes(sample = fc_enrich_window)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ treatment + channel) +
  theme_bw()

# Homogeneity of variance
fc_window %>%
  group_by(channel) %>%
  levene_test(fc_enrich_window ~ treatment)

```

### Statistics

```{r window_stats, echo = TRUE, warning = FALSE, message = FALSE}

stats_wilcox_window <- fc_window %>%
  group_by(channel) %>%
  wilcox_test(fc_enrich_window ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox_window

stats_ttest_window <- fc_window %>%
  group_by(channel) %>%
  t_test(fc_enrich_window ~ treatment) %>%
  group_by(channel) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_ttest_window

```

---

## Export plots and stats

```{r export_outputs}

today      <- format(Sys.Date(), "%y%m%d")
output_dir <- "../03_output"
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

ggsave(file.path(output_dir, paste0(today, "_boxplot_window.svg")), plot = d_window,
       width = 12, height = 7)
ggsave(file.path(output_dir, paste0(today, "_linescan_individual.svg")), plot = normalized_linescan,
       width = 14, height = 12)
ggsave(file.path(output_dir, paste0(today, "_mean_signal_linescan.svg")), plot = a,
       width = 14, height = 12)

write_csv(stats_wilcox_window, file.path(output_dir, paste0(today, "_wilcoxon_stats_window.csv")))
write_csv(stats_ttest_window, file.path(output_dir, paste0(today, "_ttest_stats_window.csv")))

cat("Exported to:", normalizePath(output_dir), "\n")

```

## Session info

```{r sessionInfo, echo = TRUE, warning = FALSE, message = FALSE}

sessionInfo()

```